\documentclass{enumerate}
\title{Constitution of Chelmsford Makerspace}
\begin{enumerate}
\section{Interpretation}
\item
	In the articles:
	\begin{description}
	\item[Chelmsford Makerspace] refers to the organisation that this article/constitution details.
	\item[Articles] refers to Chelmsford Makerspace's Articles of Association, and is in addition to them, although they don't exist as of yet.
	\item[The Committee] refers to those on the Committee board at Chelmsford Makerspace. There is no official committee at this time, but will be officiated at a later date.
	\item[The Space] refers to the physical area, building or buildings leased or purchased by Chelmsford Makersapce.
	\item[Committee Member] refers to members that are either leading or ensured with the running of Chelmsford Makerspace. Currently, Ben Orrin and Richard Raybould are the only "official" members of the Chelmsford Makerspace Committee.
	\item[Member] refers to any person that is currently a member of Chelmsford Makerspace.
	\item[Vote] refers to the democratic vote of the members of Chelmsford Makerspace.
	\item[Secretary] refers to the person appointed to perform the duties of the secretary of Chelmsford Makerspace.
	\item[NFC/RFID System] refers to the NFC security/sign in/signout system to be incorporated into the space in the future.
	\item[Guests] refers to induviduals outside of Chelmsford Makerspace that either attend the Open Tuesday Hack Night or attend any other Chelmsford Makerspace workshop or event without official member status.
\section{Committee Members}
\item
	1.1 Committee Members have the final verdict on any subject of debate, taking into consideration the vote of the members of Chelmsford Makerspace.
	1.2 A Committee Member's term of office is unending until decided otherwise, whether that be due to the decision to step down by a Committee Member themselves, the departure of a Committee Member from Chelmsford Makerspace or a vote by the Committee that a member is to step down from the Committee.
	1.3 There is no guideline to the number of members on the Committee at this time, but the likeliness is it will be below 10.
	1.4 The Committee can vote any member that wishes to join in, taking in the consideration the vote of the members of Chelmsford Makerspace, as per section 4.4.3.
	1.5 Specfic roles will be decided at a later date.
	1.6 Committee Members will be entrusted with manual key access for the space as well as the regular NFC/RFID tag for the NFC system that a regular member is given.
	1.7 Committee members are subject to the same fees as everyone else.

\section{Members}
\item
	2.1 Members of Chelmsford Makerspace are entitled to democratically vote on any decisions flagged up by the committee or indeed any idea proposed to Chelmsford Makerspace by other members.
	2.2 Each and every member of Chelmsford Makerspace must pay a fee towards the running of the organisation (This may be variable based on, but not limited to, the health of the organisation, the size of member base and the situations of individual members).
	2.3 Payment of the membership entitles a member to unlimited use of the space and free entry to any open hack night or open workshop. However, a member can still donate more money to the running of Chelmsford Makerspace if they wish to, although there will be no inclination.
	2.4 Members of Chelmsford Makerspace are entitled to fufill their duty as a member of the organisation. These duties are:
		2.4.1 For every member to clean up their mess (Including washing up their own cutlery at the end of the night, putting away tables and chairs that they have gotten out) at the end of any open hack night, workshop or when they visit the space of their own accord.
		2.4.2 For every member to be obliged to commit themselves to tasks asked of them by members of the committee. This applies to cleaning the floor, taking out rubbish and any other chores associated with the keeping of the space.
		2.4.3 For every member to make guests of Chelmsford Makerspace feel welcome and to explain to them "Who we are" and "What we do".
		2.4.4 For every member to set a good impression of Chelmsford Makerspace. This refers to the material/content posted on any digital platform associated with Chelmsford Makerspace, anything said in person about Chelmsford Makerspace and indeed the actions of a member at any open hack night or open workshop that Chelmsford Makerspace runs.
		2.4.5 To contribute accordingly to the theme of any given workshop night and refrain from playing games and or dolan memes or indeed anything of that nature that detracts from the subject matter of the workshop. This does not apply to the open Tuesday hack nights, but in the precense of guests, discretion obligated, as per 2.4.4.
	2.5 Members of Chelmsford Makerspace may be given elevated roles at a later date without being part of the Committee. This could be anything from head of a project, to chief bin emptier (If a member feels that they wish do a job for other members of the space). These roles can be chosen by the members of Chelmsford Makerspace or appointed by The Committee, with consent of the member.
	2.6 Each and every new member will be given a membership pack which contains the essentials for a member of Chelmsford Makerspace.
	2.7 Each and every member will be given access to an NFC/RFID tag to enter the space, via the NFC/RFID system. This will also account for other tasks at a later date. As a holder of an NFC/RFID tag, a member is obligated to abide these rules:
		2.7.1 As a member of Chelmsford Makerspace, their NFC/RFID tag must be kept within their possession at all times. 
		2.7.2 Access given to the space via an NFC/RFID tag to a guest by a member of Chelmsford Makerspace is forbidden. 
		2.7.3 Guests brought into the space by members are the responsibility of that member and are directly accountable for any of their actions.
		2.7.4 One NFC/RFID tag will be given to each and every member as part of the membership pack. Loss of this tag will incur a small fee for a new one.
	2.8 All members must refer to James Hyland as "Skidland", "Skidster", "Skidmark", "Skiddie", "Skids", or any other derogatory name involving the word "Skid" at all times.
\section{Guests}
\item
	3.1 Guests are not in any way part of Chelmsford Makerspace, nor do they represent Chelmsford Makerspace.
	3.2 Guests are subject to all flexible fees charged at any open hack night/workshop that they attend. The current rate for open hack nights is £2.50.
	3.3 Payments made on these events are for access to the space for only the length of the event's period.
	3.4 It is the duty of members of Chelmsford Makerspace to welcome guests to Chelmsford Makerspace as per 2.4.3.
	3.5 Actions of guests are not the responsibility of Chelmsford Makerspace on open hack nights or workshops. Guests are accountable for themselves on any open Makerspace event.
	3.6 In the event that a guest is introduced into the space by a member outside of open times, the member is responsible for the guest as per 2.7.3.
\section{General Meetings}
\item
	4.1 An Annual General Meetings (AGM) will take place every calender year in September (not particularly specific as of now).
	4.2 An Extraordinary General Meeting (EGM) can be called by the majority of the Committee or members of Chelmsford Makerspace.
	4.4 EGMs will have one specific subject matter and can be called at any time.
	4.4 Committee Meetings (CM) will be held at least one every month or two. These meetings are done only with the members on the Committee and those members only.
	4.5 Elections
		4.5.1 During an AGM, elections will be held for the committee for any members who wish to step up or to replace those who wish to step down, although there is no set number of committee members so a replacement may not be required. A trustees term is unending until they either step down or are voted out of office by a majority vote of the committee, as per and in addition to section 1.2.
		4.5.2 Any member can stand for election to be part of the committee. 72 hours of notice must be given that a member is going to stand for election.
		4.5.3 All members of Chelmsford Makerspace have the right to a vote, but the Committee can overrule if need be. This is only likely to be under extraordinary circumstances (Skidland getting voted in as an example).
		4.5.4 Any member can only vote once for once candidate.
		4.5.5 Votes will be collected in secret by an elected committee member or member of the Makerspace.
		4.5.6 Members can abstain from voting.
		4.5.7 Proxy votes will be allowed for for members who cannot attend the AGM. It is not compulsary for all members to vote, as of 4.5.6. It is only compulsary for all members who wish to to be given the opportunity to vote. Proxy votes will take place within 48 hour preceeding the AGM.
		4.5.8 In the event of a draw, a new vote will be called with the number of tying members. This vote will be done by proxy.
		4.5.9 Although the vote by Chelmsford Makerspace is democratic, the leading supervisors of the Makerspace are permenant members unless they step down. 
		4.5.10 Details of the AGM must be made available to all Makerspace members at least 7 days prior to the meeting itself.
		4.5.11 Chelmsford Makerspace reserves the right to reject any member, project, idea etc. if it violates the constitution or if it is not in the best interests of the group.
	4.6 20% of the members of Chelmsford Makerspace must attend in order for an AGM to go ahead. In the event that they don't, it will be rearranged for another date.
\section{Terminations}
\item
Membership may be terminated if:
	5.1 A member dies or, if it is an organisation, ceases to exist (Skidland gets abducted by aliens unbeknownst to the rest of the members or indeed anyone on planet Earth).
	5.2 A member resigns giving adequate notice to the Committee.
	5.3 A member fails to pay the full amount of a fee required within 6 weeks of their failure to pay. A minimum of one formal written reminder will be sent within that time.
	5.4 A member is removed from membership by a resolution of the Committee that is in the best interests of Chelmsford Makerspace that their membership is terminated. A resolution to remove a member from membership may only be passed if:
		5.4.1 The member has been given sufficient notice of the Committee's decision, with a full explanation of the reasons as to why their membership is to be terminated.
